Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-24 writeup/gz_hubble_data.tex
Text on image creation and galaxy selection

%\documentclass[twocolumn]{emulateapj}
%\documentclass[12pt,preprint]{aastex}

\documentclass[usenatbib]{mn2e}

\newcommand{\s}{$_{\rm s}$}
\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\msun}{{\it M}$_{\odot}$}
\newcommand{\lsun}{{\it L}$_{\odot}$}
\newcommand{\mear}{{\it M}$_{\oplus}$}
\newcommand{\etal}{{\it et al.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\eg}{{\it e.g.}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\magarc}{{\rm mag\,arcsec$^{-2}$}}
\newcommand{\MK}{{{\rm M}_{\rm ext,K}-5\log h}}
\newcommand{\ri}{{$r_{21}$}}
\newcommand{\ra}{$R_A$}
\newcommand{\vobs}{{v_{\rm obs}}}
\newcommand{\kmsMpc}{km~s$^{-1}$ Mpc$^{-1}$}
\newcommand{\h}{$h_{70}$}
\newcommand{\vpec}{v_{\rm pec}}
\newcommand{\like}{{\mathcal L}}
\newcommand{\vs}{\vspace*{5pt}}
\newcommand{\continued}{ (Continued)}

\newcommand{\ferengi}{\textsc{ferengi}}
\newcommand{\sextractor}{\textsc{sextractor}}

% Journals
%\newcommand{\mnras}{MNRAS}
%\newcommand{\apj}{ApJ}
%\newcommand{\apjl}{ApJL}
%\newcommand{\aj}{AJ}
%\newcommand{\pasp}{PASP}
%\newcommand{\aaps}{A\&AS}
%\newcommand{\aap}{A\&A}
%\newcommand{\apjs}{ApJS}
%\newcommand{\araa}{ARA\&A}
\newcommand{\pbar}{p_{\rm bar}}
\newcommand{\pfeatures}{p_{\rm features}}
\newcommand{\fHI}{f_{\rm HI}}

% Bands

\newcommand{\Bband}{$B_{435W}$}
\newcommand{\Vband}{$V_{606W}$}
\newcommand{\iband}{$I_{775W}$}
\newcommand{\Iband}{$I_{814W}$}
\newcommand{\zband}{$I_{850LP}$}

@@

@@

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
%
% List of people who have contributed (not sure if everyone will be author)
% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski
% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
% Tech: Smith, Parrish, Simpson, other devs?
% External: Han, Griffith
%
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

@@

Space-based observatories, particularly the \textit{Hubble Space Telescope}, have been responsible for the bulk of imaging studies of high-redshift galaxies. Observations of fixed fields with very deep imaging \citep[eg,][]{gia04,dav07,gro11,sco07,bec06,wil96} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology. While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \textit{HST} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures. Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \textit{HST} \citet{che12}. The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.

@@

This paper presents the results from the Galaxy Zoo Hubble (GZH) project. GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \textit{Hubble Space Telescope}.

@@

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below. The majority of the images (as implied by the project name) are taken directly from \textit{Hubble Space Telescope} Legacy Surveys,

\subsection{Summary of HST Legacy Survey Imaging}

\begin{itemize}
\item Hubble ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories. The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$. Images were in two bands, with exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.

@@

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}28^\textrm{s}, \delta=+02^\circ12^\prime21^{\prime\prime}$. Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories. The Hubble ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\% completeness magnitude for a galaxy with a half-light radius of $0^{\prime\prime}.50$ in \Iband{} is 24.7 mag.

@@

@@

The GOODS images in GZH use mosaics constructed from both 2-epoch and 5-epoch sets of data.

The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.

We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S (Figure~\ref{fig:filtercurves}).

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \textit{HST} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

Fake AGN

Stripe 82

Different treatment of colored noise in COSMOS; creating color gradients with Subaru data and using \Iband{} for illumination map.

FERENGI images.

@@

We compiled redshifts from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC. We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

\begin{figure*}
\includegraphics[width=160mm]{figures/specz_comparison.pdf}
\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
\label{fig:speczs}
\end{figure*}

\tabletypesize{\scriptsize}
\begin{deluxetable}{l|rr|rrr|rr|r|rr}
\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{Griffith}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

%-----------------------------------------------------------------------------------------------------------------------------------
%\begin{figure}
%\begin{center}
%\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
%\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshifting.\label{fig:exampleFERENGI}}
%\end{center}
%\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

In order to test and correct for the effects of redshift, we generated a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the HST surveys out to $z=1$. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original HST images.

@@

We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code. The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in HST imaging.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{fig:exampleFERENGI}}
\end{figure*}

@@

\begin{equation}
\log_{10}(\hat\zeta) = \zeta_0 + \zeta_1 \times \mu,
\label{eqn:zetafit}
\end{equation}

@@

\begin{figure*}
\centering
\subfigure{[6a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
\subfigure{[6b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
\\
\subfigure{[6c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
\subfigure{[6d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. [6a]: Each point in a given redshift and surface brightness bin represents a unique galaxy. On the y-axis in each bin is the $p_{\rm features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the x-axis is the $p_{\rm features}$ value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents $p_{\rm features,z}$ = $p_{\rm features,z=0.3}$. Regions in which there is a single-valued relationship between $p_{\rm features}$ at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. [6b]: A larger version of the dark-outlined square in [6a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [6c]: The same data as [6a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic $p_{\rm features,z=0.3}$ for a given range of observed $p_{\rm features,z}$ values. In each sub-bin, the orange bars represent the inner 80th percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values. [6d]: The same data as [6b], but highlighting the upper and lower limit regions.}
\label{fig:p_vs_p}
\end{figure*}

>>>>

%\documentclass[twocolumn]{emulateapj}
%\documentclass[12pt,preprint]{aastex}
\documentclass[usenatbib]{mn2e}

@@

\input{gzh_macros.tex}

@@

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
%
% List of people who have contributed (not sure if everyone will be author)
% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
% Tech: Smith, Parrish, Simpson, other devs?
% External: Han, Griffith
%
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

@@

Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies. Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology. While these measurements are helped by the fact that the angular diameter distance is relatively flat at $z>1$ in a flat $\Lambda$CDM cosmology, the scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve much of the structure for a Milky Way-sized galaxy (at least for distinguishing a disk from a bulge), but will be limited for more compact structures. Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the more compact sizes of earlier galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}. The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.

@@

This paper presents the results from the Galaxy Zoo Hubble (GZH) project. GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.

@@

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria, which we describe below. The majority of the images (as implied by the project name) are taken directly from \hst{} Legacy Surveys.

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

\subsection{Summary of Hubble Legacy Survey Imaging}\label{ssec:legacy_surveys}

\begin{itemize}
\item \hubble{} ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories. The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$. Images were in two bands, with exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.

@@

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}28^\textrm{s}, \delta=+02^\circ12^\prime21^{\prime\prime}$. Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories. The \hst{} ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\% completeness magnitude for a galaxy with a half-light radius of $0^{\prime\prime}.50$ in \Iband{} is 24.7 mag.

@@

\subsection{Galaxy selection}

For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of SExtractor \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}. We select all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source. Of the images in the coadded sample, 5144/30339 (17 percent) are dimmer than this initial magnitude cut.

@@

The images used for classification in GZH are color-composite JPGs made from multi-band data. The exact process for creating the images depends on the bands and resolutions in the surveys.

For galaxies in the ACS General Catalogue \citep[AEGIS, COSMOS, GEMS, 2-epoch GOODS;][]{gri12}, the color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively. We also apply a nonlinear mapping to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:

\begin{equation}
I_\mathrm{channel,new} = I_\mathrm{channel,old} \times \frac{\arcsinh(b\times r)}{(b\times r)}
\label{eqn:nonlinear}
\end{equation}

\noindent We adopt a value of $b=3$ for the \hst{} images in \citet{gri12}.

Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when GZH was launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. Note that the 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

By the time that the 5-epoch sets of GOODS data were put into GZH, coverage in four separate \hst{} bands had become publicly available. The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband in the blue channel, \Iband{} in the red channel, and \zband in the green channel. These images also had the speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH. For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}. This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0\arcsec.95 and 1\arcsec.05 \citep{tan07}.

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The coadded Stripe~82 images were assembled from runs (106,206) in DR7 and generated into JPGs using the method of \citet{lup04}.

To address a number of images in which the sky noise was highly colored (which might have been a distraction to users), we apply a soft-edged object mask to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky. This technique was applied only to the coadded Stripe~82 and the COSMOS images.

\subsection{Artificial AGN}

We also created a set of images designed to measure the effect of AGN on morphological classifications. Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic the effect of a strong bulge. The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy. For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images with different simulated AGN for each chosen host.

Two sets of simulated AGN were generated in GZH. The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}. The second set (version~2) was assembled from 96~galaxies in GOODS-S; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.

\subsection{Artifically-redshifted images}

FERENGI images (ask Edmond to write this?) Should contain much of the information in \S\ref{sec:debiasing} right now.

@@

We compiled redshifts from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the ACS-GC, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the ACS-GC. we use that, else 3DHST, else MUSYC. We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (ACS-GC, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

\begin{figure*}
\includegraphics[width=160mm]{figures/specz_comparison.pdf}
\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
\label{fig:speczs}
\end{figure*}

\tabletypesize{\scriptsize}
\begin{deluxetable}{l|rr|rrr|rr|r|rr}
\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{ACS-GC}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

In order to test and correct for the effects of redshift, we generated a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the \hst{} surveys out to $z=1$. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original \hst{} images.

@@

We selected 288 unique galaxies from SDSS imaging to run through the \ferengi{} code. The selection spanned a variety of galaxy morphologies (as selected by GZ2 classifications) and $r^\prime$-band surface brightnesses, and also spanned the redshift range of SDSS targets (in $N_z = 4$ bins) in order to be optimised for different target minimum redshifts in \hst{} imaging.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated \hst{} images. The value of \pfeatures{} for each panel is (1) Top row: \pfeatures~= 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: \pfeatures~= 1.00, 0.875, 0.875, 0.625, 0.375. \label{fig:exampleFERENGI}}
\end{figure*}

@@

\begin{equation}
\log_{10}(\hat\zeta) = \zeta_0 + (\zeta_1 \times \mu),
\label{eqn:zetafit}
\end{equation}

@@

\begin{figure*}
\centering
\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
\\
\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy. On the y-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the x-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents \pfeaturesz=\pfeaturesrest. Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values. In each sub-bin, the orange bars represent the inner 80th percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values. [d]: The same data as [b], but highlighting the upper and lower limit regions.}
\label{fig:p_vs_p}
\end{figure*}
